Example Paper

### 2021-07-07 latex-article/article.tex
Update footnotes

See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat}, appendix table \ref{reg1}, and citation \citet{Eigen1971}.

@@

\begin{theorem}[Example Theorem]\label{residue_thm}
    This is an example theorem \[ 
        \hat{\beta}=\frac{\sum_{\ell}e_{\ell}z_{\ell}y_{\ell}^{\perp}}{\sum_{\ell}e_{\ell}z_{\ell}x_{\ell}^{\perp}}
    \]
\end{theorem}

Example numbered and non-numbered equations
\begin{equation}\label{fe_reg}
    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t} 
\end{equation}

@@

\begin{table}[tb] 
    \caption{Summary Statistics (tabularx)}
    \label{summ_stat}

@@

\begin{table}[tb] 
    \caption{Regression Results (Custom tabularx widths)} 
    \label{reg1}

>>>>

See below for Theorem \ref{thm:residue_thm}, for the regression specification (\ref{eq:fe_reg}), and for \autoref{tab:summ_stat}, appendix \autoref{tab:reg1}, and citation \citet{Eigen1971}.

@@

\begin{theorem}[Example Theorem]\label{thm:residue_thm}
    This is an example theorem \[ 
        \hat{\beta}=\frac{\sum_{\ell}e_{\ell}z_{\ell}y_{\ell}^{\perp}}{\sum_{\ell}e_{\ell}z_{\ell}x_{\ell}^{\perp}}
    \]
\end{theorem}

Example numbered and non-numbered equations
\begin{equation}\label{eq:fe_reg}
    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t} 
\end{equation}

@@

\begin{table}[tb] 
    \caption{Summary Statistics (tabularx)}
    \label{tab:summ_stat}

@@

\begin{table}[tb] 
    \caption{Regression Results (Custom tabularx widths)} 
    \label{tab:reg1}
